Efficient Handling of String-Number Conversion

### 2019-11-22 draft.tex
add decode and encode for PA

Through the paper, we will use quantifier-free linear integer arithmetic formulae, and call them \emph{linear formulae} for short.  
Given a linear formula $\phi$ over variables $V$ and an \emph{integer interpretation} of $V$, a function $I:V\rightarrow \integers$, 
we denote by $I\models \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$. 
We use $\modelsof \phi$ to denote the set all models of $\phi$ \changed{and use $\modelsof \phi_{V'}$ to denote the same set but projected to the domain $V'$}.%
%Let $J$ and $J'$ be two sets integer interpretations, $J$ containting interpretation of variables $V$ and $J'$ of variables $V'$. 
%We say that $J$ and $J'$ are \emph{equivalent}, written $J\iequiv J'$, if their interpretations restricted to the common variables are the same, that is, if 
%$\{\restrict I {V\cap V'} \mid I \in J\} = \{\restrict {I'} {V\cap V'} \mid I' \in J'\}$. We may write $J\eqwrt{V\cap V'} J'$ if we wish to made the common variables explicit.

@@

Parametric automata accept words over $\cvar$, called \emph{parametric words}, but we still use them as representations of languages over $\Sigma$. 
%
Namely, words over $\cvar$ are interpreted as words over $\Sigma$ under an
\emph{interpretation of $\cvar$},
%
a mapping $I:\cvar\rightarrow\Sigma_\epsilon$ (recall that $\Sigma_\epsilon \subseteq \nat$). 
For a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, its interpretation $I(x)$ is then defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
%
%We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, 
%the semantics of a language $L\subseteq V^*$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, 
We then define the semantics of the PA $P$ as the set of strings   
$\semof {\pa} = \{I(x) \mid x\in L(A),I\in\semof \paf\}$ of all interpretations satisfying $\paf$ of all parametric strings in the language of $A$. 
\yfc{I just found that we have not defined the restriction of the domain of functions such as $e_{V}$,  maybe need it somewhere. }

\yfc{Some attempts to define both encodes and decodes of PA, need more explanation of why we define them I guess. It is planed to be a replacement of the text below him. One interesting observation: the definitions of both are almost the same
	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
	}
\changed{
	Observe that every word $w \in \semof{\pa}$ is uniquely determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}$ such that $w = I(x)$. We call the union of $I$ and the Parikh image $\parikhof{x}$ a \emph{word encoding} of $w$ in $\pa$. More formally, a wording encoding of $\pa$ is mapping of the type $\cvar\cup\#\cvar \rightarrow \nat$ and the set of word encodings of $w$ in $\pa$ is defined as $\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$. For every word encoding $e\in \encode \pa( w )$, there must be a parametric word $x\in L(P)$ and some valid character assignment $I\in \semof \paf$ such that $I(x) =w$ and $e= I \cup \parikhof{x}$. When $e\in \encode \pa( w )$, we also say it \emph{$\pa$-encodes} $w$. We lift the encoding function $\encode \pa$ to set of word $W$ by defining  $\encode \pa(W) = \bigcup_{w\in W} \encode \pa(w)$.

>>>>

Through the paper, we will use quantifier-free linear integer arithmetic formulae, and call them \emph{linear formulae} for short.  
Given a linear formula $\phi$ over variables $V$ and an \emph{integer interpretation} of $V$, a function $I:V\rightarrow \integers$, 
we denote by $I\models \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$. 
We use $\modelsof \phi$ to denote the set all models of $\phi$.%
%Let $J$ and $J'$ be two sets integer interpretations, $J$ containting interpretation of variables $V$ and $J'$ of variables $V'$. 
%We say that $J$ and $J'$ are \emph{equivalent}, written $J\iequiv J'$, if their interpretations restricted to the common variables are the same, that is, if 
%$\{\restrict I {V\cap V'} \mid I \in J\} = \{\restrict {I'} {V\cap V'} \mid I' \in J'\}$. We may write $J\eqwrt{V\cap V'} J'$ if we wish to made the common variables explicit.

@@

Parametric automata accept words over $\cvar$, called \emph{parametric words}, but we still use them as representations of languages over $\Sigma$. 
%
Namely, words over $\cvar$ are interpreted as words over $\Sigma$ under an
\emph{interpretation of $\cvar$},
%
a mapping $I:\cvar\rightarrow\Sigma_\epsilon$ (recall that $\Sigma_\epsilon \subseteq \nat$). 
For a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, its interpretation $I(x)$ is then defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
%
%We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, 
%the semantics of a language $L\subseteq V^*$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, 
We then define the semantics of the PA $P$ as the set of strings   
$\semof {\pa} = \{I(x) \mid x\in L(A),I\in\semof \paf\}$ of all interpretations satisfying $\paf$ of all parametric strings in the language of $A$.

\hide{Some attempts to define both encodes and decodes of PA, need more explanation of why we define them I guess. It is planed to be a replacement of the text below him. One interesting observation: the definitions of both are almost the same
	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
	}
\changed{
The function $\encode \pa$ below encodes a word $w$ to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
Informally, a word encoding $e\in \encode \pa( w )$ means $w$ corresponds to a parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $e$. Since $e$ has only the information of number of occurrences of character variables (Parikh image), the same word encoding may be shared by multiple word, as formalized in the definition of $\decode \pa(e)$. For the case that $\pa$ is flat, by Lemma~\ref{lemma:decoding} each word encoding $e\in \encode \pa( w )$ uniquely encodes the word $w$. The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
}

\hide{
	Observe that every word $w \in \semof{\pa}$ is uniquely determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}$ such that $w = I(x)$. We call the union of $I$ and the Parikh image $\parikhof{x}$ a \emph{word encoding} of $w$ in $\pa$. More formally, a wording encoding of $\pa$ is mapping of the type $\cvar\cup\#\cvar \rightarrow \nat$ and the set of word encodings of $w$ in $\pa$ is defined as $\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$. For every word encoding $e\in \encode \pa( w )$, there must be a parametric word $x\in L(P)$ and some valid character assignment $I\in \semof \paf$ such that $I(x) =w$ and $e= I \cup \parikhof{x}$. When $e\in \encode \pa( w )$, we also say it \emph{$\pa$-encodes} $w$. We lift the encoding function $\encode \pa$ to set of word $W$ by defining  $\encode \pa(W) = \bigcup_{w\in W} \encode \pa(w)$.
